Review of the Literature on Exact Formulas for Mediation Effects

### 2024-05-24 notes/Literature_Review/Literature Review.tex
Re-organize directory

@@

@@

\subsubsection{UQ for Group-Level Effects}

>>>>

I'm just finishing-up my code for the binary response, binary mediator, mixed effects case. My analysis is running, but the output doesn't look right so I need to do some debugging.

I now better understand the uncertainty quantification method used by the Imai group. See Section \ref{sec:Imai_UQ} for details. Briefly, they do a Monte Carlo analog of the $\delta$-method. If the target of inference is a function of some model parameters, they start by estimating the sampling distribution of our estimator for those model parameters. They then simulate from this estimated sampling distribution and evaluate the function of interest on each simulated observation. This produces a sample from the pushforward measure induced on the target of inference by our estimated sampling distribution for the model parameters. It's not completely clear to me how they generate confidence intervals from the Monte Carlo samples, but they call their method ``quasi-Bayesian'', so I suspect it's just percentile intervals.

Incidentally, if we could do exact (i.e. non-asymptotic) distribution theory for the model parameter (e.g. ordinary linear regression), then Imai's method is equivalent to the parametric bootstrap. They just skip the generation of datasets and work directly with the bootstrap distribution of the estimator.

@@

I think that at this week's meeting, we should plan out what we want to put in the paper. I propose that we do total, direct and indirect effects on risk difference, risk ratio and odds ratio scales, but stick to fixed-effects (i.e. avoid predicting group-level effects). Based on other work in the literature. I think that's enough for a paper, provided that we do a nice Monte Carlo study comparing our UQ with other methods, such as Imai's quasi-Bayesian method, the weighting method of \citet{Lan12} and the imputation method of \citet{Van12}. All of these methods are implemented to varying extents in \texttt{R} packages, \texttt{mediation} for the former and \texttt{medflex} for the latter two.

Prediction of group-level effects barely comes up in the literature. The \texttt{mediation} package from Imai's group does it, but with very little discussion. They give a few sentences in the package vignette saying they can do group-level effect prediction, but don't give any further discussion or references. I had to read their source code to know what method they're using. Prediction of group-level mediation effects seems like an untapped area that we are well-positioned to develop.

@@

\subsubsection{UQ for Group-Level Effects}
\ref{sec:Imai_UQ}
